Parameter estimation

### 2023-05-04 SFE-article/Article_Model_Parameters.tex
03.05
04.05

\section{Conclusions}

@@

@@

\clearpage
\onecolumn
\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}

\begin{figure*}[!h]
	%\centering 
	\includegraphics[trim=0cm 6cm 0cm 0cm, clip,height=0.85\textheight]{Sections/ultraReportT5.pdf}
	\caption{The result of solid density measurement}
\end{figure*}

>>>>

\section{Conclusions}
In this work, a dataset obtained from experiments conducted at various temperature and pressure was utilized for parameter estimation to develop a process model. The model showed good agreement with experimental yield curves for the extraction of caraway oil from caraway seeds. Linear and non-linear regression techniques were employed to establish correlations for the internal diffusion coefficient and axial diffusion coefficient in terms of fluid density. These correlations allowed for the generalization of the process model to a range of operating conditions, specifically temperature ranging from $40^\circ C$ to $50^\circ C$, pressure ranging from 200 bar to 300 bar, and flow rate of 0.4 l/min (with flow variations up to 5\%). The generalized model can be used to evaluate the impact of different operating conditions on the extraction yield or for economic analysis of the extraction process.

@@

\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}

\begin{figure}[!h]
	\centering 
	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
	\caption{The result of solid density measurement}
\end{figure}

@@

### 2023-05-04 SFE-article/Sections/Results.tex
04.05

	The other two parameters ($D_i$ and $D_e^M$) are subject to regression to obtain correlations in terms of density. Figure \ref{fig:Regression} shows the first- and second-order polynomials used to fit $D_i$ and $D_e^M$ as a function of fluid density. Interestingly, these two parameters exhibit opposite behavior. The internal diffusion coefficient increases with increasing fluid density, whereas the axial diffusion coefficient decreases.

	\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[trim = 10.5cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
		\caption{First order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
	\end{subfigure}
	\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[trim = 10.5cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
		\caption{Second order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
	\end{subfigure}
	\caption{Results of parameter fitting, with estimation of the initial state} 
	\label{fig:Regression}
	\end{figure}

>>>>

	The other two parameters ($D_i$ and $D_e^M$) are subject to regression to obtain correlations in terms of density. Figure \ref{fig:Regression} shows the first- and second-order polynomials used to fit $D_i$ and $D_e^M$ as a function of fluid density. Interestingly, these two parameters exhibit opposite behavior.

	\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[trim = 10.5cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
		\caption{First order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
		\label{fig:Regression_1}
	\end{subfigure}
	\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[trim = 10.5cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
		\caption{Second order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
		\label{fig:Regression_2}
	\end{subfigure}
	\caption{Results of parameter fitting, with estimation of the initial state} 
	\label{fig:Regression}
	\end{figure}

	The results of the linear regression applied to $D_i$ and $D_e^M$ are presented in Figure \ref{fig:Regression_1}. It can be observed that the internal diffusion coefficient increases with increasing fluid density, while the axial diffusion coefficient decreases.

	The increase in the density of the supercritical fluid can lead to an increase in the solubility of the solute and, consequently, an increase in the concentration gradient. This increased concentration gradient drives the solute to diffuse more rapidly through the matrix of the solid particles, resulting in an increase in the internal mass transfer coefficient. However, the effect of increased solubility on the internal mass transfer coefficient is greater than the resistance coming from higher density, resulting in an overall increase in the internal mass transfer coefficient with density.

	The behaviour of the axial diffusion coefficient can be explained through Graham’s Law of Diffusion, which states that the rate of diffusion of a molecule is inversely proportional to the square root of its density under given conditions of temperature and pressure. This means that denser media slow down the axial diffusion rate of molecules.

	{\color{red}IDEAL I SHOULD SUPPORT THIS EXPLANATION WITH SOME REFERENCES}

	Figure \ref{fig:Regression_1} show the result of fitting a second-order polynomial in density space. It can be observed that the fit obtained from quadratic functions seems to be represent both dataset better.

### 2023-05-04 SFE-article/Sections/Thermodynamic_details.tex
04.05

	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term {\color{red}REF}. In the following, we report only the main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$: Step-by-step derivations using the Peng-Robinson's equation are given. \todo{Add step-by-step derivation} \\

	At given temperature and pressure, for $\text{CO}_2$ we have

>>>>

	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}. In the following, we report only the main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$:
